Ames Housing: 허위매물 탐지 프로젝트

### 2025-04-25 group1.qmd
ㄴㅇㄹㄴㅇㄹ

| 가격 구간 | 평균 가격  (USD) | 주요 지역 |
|----|----|----|
| 🔺 **고가 지역 (High)** | ≥ 217,676 | NoRidge, NridgHt, StoneBr, Veenker, Greens, Timber |
| ⚖️ **중간 지역 (Mid)** | 136,144 \~ 217,675 | CollgCr, Mitchel, NAmes, SawyerW, OldTown, Crawfor, Edwards |
| 🔻 **저가 지역 (Low)** | ≤ 136,143 | MeadowV, BrDale, IDOTRR, Landmrk, Blueste |

>>>>

| 가격 구간 | 기준(분위수) | 주요 지역 |
|----|----|----|
| 🔺 **고가 지역 (High)** | 상위 25% (≥ 75th percentile) | NoRidge, NridgHt, StoneBr, Veenker, Greens, Timber |
| ⚖️ **중간 지역 (Mid)** | 중간 50% (25th~75th percentile) | CollgCr, Mitchel, NAmes, SawyerW, OldTown, Crawfor, Edwards |
| 🔻 **저가 지역 (Low)** | 하위 25% (≤ 25th percentile) | MeadowV, BrDale, IDOTRR, Landmrk, Blueste |
